\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Cost-performance ratio for object detection}

\author{\IEEEauthorblockN{Isaías Labrador Sánchez}
\IEEEauthorblockA{\textit{dept. of science} \\
\textit{EAFIT}\\
Medellín, Colombia \\
ilabradors@eafit.edu.co}
\and
\IEEEauthorblockN{Juan Manuel Young Hoyos}
\IEEEauthorblockA{\textit{dept. of science} \\
\textit{EAFIT}\\
Medellín, Colombia \\
jmyoungh@eafit.edu.co}
}

\maketitle

\input{sections/abstract.tex}

\begin{IEEEkeywords}
Numeric methods, C++, Python, algorithms, insert
\end{IEEEkeywords}

%%! Sections
\input{sections/introduction.tex}
\input{sections/objectives.tex}
\input{sections/theoretical_framework.tex}
\input{sections/dummy.tex}

\begin{thebibliography}{00}
\bibitem{b1} Burden, Richard L. and Faires, Duglas. Análisis Numérico. Editorial Thomson. 9 Edición 2011.
\bibitem{b2} Chapra, S. and Canale, R., 2003. Numerical methods for engineers. Boston: McGraw-Hill.
\bibitem{b3}L. Dalcin, et al.,"Cython: The Best of Both Worlds" in Computing in Science  Engineering, vol. 13, no. 02, pp. 31-39, 2011.doi: 10.1109/MCSE2010.118
\bibitem{4} A Brief Description - C++ Information", Cplusplus.com, 2021. [Online]. Available: https://www.cplusplus.com/info/description/.
\bibitem{5} Python vs C++ Comparison: Compare Python vs C++ Speed and More", BitDegree.org Online Learning Platforms, 2021. [Online]. Available: https://www.bitdegree.org/tutorials/python-vs-c-plus-plus/.
\end{thebibliography}

\end{document}
